Implementing Real-time Transport Services over an Ossified Network

### 2016-05-16 paper.tex
Expand Real-time Transport Services

\newcommand{\todo}[1]{\textbf{\textcolor{red}{To do: #1}}}

@@

..what a conceptual API for this would look like?

>>>>

\newcommand{\todo}[1]{\textbf{\textcolor{red}{To do -- #1}}}

@@

We note that a connection-oriented transport is not a core requirement for
many real-time multimedia applications.  Indeed, flexibility to change the
destination of data within a call could be beneficial for applications that
support mobile users, or for some forms of multiparty session. However, to
support NAT traversal and to help dynamically manage firewall pinholes, it
is often desirable for the transport to be connection oriented. We find
these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service. 
Similarly, while not strictly needed by the applications, it is beneficial
if the transport provides a keep-alive service to refresh NAT and firewall
bindings if the application goes silent.

Table \ref{tab:services} summarises the transport services required for
real-time multimedia applications.

\begin{table}
  \centering
  \begin{tabular}{ll}
    \toprule
      Transport Service     & Requirement \\
    \midrule
      Deadlines             & Core        \\
      Partial reliability   & Core        \\
      Dependencies          & Core        \\
      Message-oriented      & Core        \\
      Sub-streams           & Core        \\
      Congestion controlled & Core        \\
      Connection oriented   & Subsidiary  \\
      Keep-alive            & Subsidiary  \\
    \bottomrule
  \end{tabular}
  \caption{Transport services required for real-time multimedia}
  \label{tab:services}
\end{table}

Given a transport protocol that provides the above services, how could the
API between transport and application be structured?

\todo{Stephen: outline the TCP Hollywood API, with text and a figure}

It is to be noted that this API is not dissimilar to the PR-SCTP abstract
API. \todo{CSP: check this}
